---
title: "BBets Project"
author: "Adreanna Morales"
date: "1/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

How much money is won/lost on a bet that at east two people have the same b'day in a class of 35. Instructor wagers 2:1 

Instructor has done this 15 times, 
1. what is his expected win/lose amount 

2. how much would the instructor have to wager tomake the bet fair

3. how many students would have to be in the class or a 2:1 bet to be fair?
    
```{r}
days = 1:365

saveArray= vector ('numeric')
for (k in 1:1000){
    bank =0
    for(i in 1:525){
      sampleClass = sample(days, 35, replace =TRUE)

    repeats = length(unique(sampleClass))
    if (repeats ==35) bank = bank - 10
    else bank = bank + 1
  }
saveArray [k]= bank
}

```
    histogram of bank amounts.
```{r}
hist(saveArray)
```

Answer questions #1
```{r}
print ('average amt:')
print (mean(saveArray))
```

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
